Cycles of the logistic map

### 2013-05-13 doc/pc.tex
remove old programs, improve nsolve
doc: rearrange references
remove some theorem environments

The cycle and its stability depend on the parameter $r$.
%
Our purpose is to present an algorithm to identify
  all regions of $r$ that allow stable $n$-cycles.

@@

\begin{remark}[1]
Here, ``minimal'' means that the polynomial contains all zeros;
  it does not, however, necessarily mean that the polynomial is irreducible.
\end{remark}

@@

%\bibitem{bailey1} D. H. Bailey and D. J. Broadhurst,
%  Parallel integer relation detection: techniques and applications,
%  \textit{Mathematics of Computation}
%  \textbf{70},
%  1719--1736
%  (2000).
%
\bibitem{bailey}
  D. H. Bailey, J. M. Borwein, V. Kapour and E. W. Weisstein,
  Ten problems in experimental mathematics,
  \textit{The American Mathematical Monthly}
  \textbf{113},
  481--509
  (2006).

>>>>

The cycle and its stability depend on the parameter $r$.
%
The problem is to identify
  all regions of $r$ that allow stable $n$-cycles,
  which has been the objective of several previous
  studies
  \cite{brown1, brown2, stephenson1, stephenson2, stephenson3,
  saha, bechhoefer, gordon, burm, zhang, bailey, kk1, lewis}.
Below we present a simple algorithm to do so.

@@

\begin{remark}[1]
Here, ``minimal'' means that the polynomial contains all zeros.
It happens to be irreducible for a general $\lambda$.
At $\lambda = 1$, the polynomial of $R$, however, can be factorized (see later).
\end{remark}

@@

\bibitem{bailey}
  D. H. Bailey and D. J. Broadhurst,
  Parallel integer relation detection: techniques and applications,
  \textit{Mathematics of Computation}
  \textbf{70},
  1719--1736
  (2000);
  D. H. Bailey, J. M. Borwein, V. Kapour and E. W. Weisstein,
  Ten problems in experimental mathematics,
  \textit{The American Mathematical Monthly}
  \textbf{113},
  481--509
  (2006).
